Detecting Hate Speech with GPT-3

### 2022-03-18 outputs/documents/paper.tex
Data collection for multiple iterations of few-shot single catgory, updates to tables in paper, begin updates to results sections

\title{Detecting Hate Speech with GPT-3 \thanks{Code and data are available at: \url{https://github.com/kelichiu/GPT3-hate-speech-detection}. We gratefully acknowledge the support of Gillian Hadfield, the Schwartz Reisman Institute for Technology and Society, and OpenAI for providing access to GPT-3 under the academic access program. We thank two anonymous reviews and the editor, as well as Amy Farrow, Haoluan Chen, John Giorgi, Mauricio Vargas Sepúlveda, Monica Alexander, Noam Kolt, and Tom Davidson for helpful discussions and suggestions. Please note that we have added asterisks to racial slurs and other offensive content in this paper, however the inputs and outputs did not have these. Comments on the 16 March 2022 version of this paper are welcome at: \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}  }

@@

@@

The overall results of the zero-shot experiments are presented in Table \ref{tab:zeroshot-summary}, and Appendix \ref{appendixbzeroshot} provides additional detail. The model has 34 matches (true positives and negatives) and 26 mismatches (false positives and negatives) in the sexist category, and 41 matches and 19 mismatches in the racist category. The model performs more accurately when identifying racist comments, with an accuracy of 68 per cent, compared with identifying sexist comments, with an accuracy of 57 per cent, but the F1 score for each type of hate speech is roughly the same. The overall ratio of matches and mismatches is 75:45. In other words, the accuracy in identifying hate speech in the zero-shot setting is 63 per cent. The model has an F1 score of 81 per cent in this setting, with a notably high recall of 87 per cent.

@@

\caption{\label{tab:zeroshot-summary}Performance of zero-shot learning in hate speech classification}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
\midrule
Racism & 68 & 67 & 73 & 70\\
Sexism & 57 & 54 & 100 & 70\\
Overall & 62 & 58 & 87 & 81\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:oneshot-summary}Performance of one-shot learning in hate speech classification}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
\midrule
Racism & 62 & 59 & 80 & 68\\
Sexism & 60 & 57 & 77 & 66\\
Overall & 61 & 58 & 78 & 65\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:fewshotsingle-summary}Performance of single-category few-shot learning in hate speech classification}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
\midrule
Racism & 68 & 66 & 77 & 71\\
Sexism & 70 & 75 & 60 & 67\\
Overall & 69 & 69 & 68 & 61\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{comparison-1.pdf}
\caption{\label{fig:comparison}Comparing classification with and without an instruction}
\end{figure}

@@

In conclusion, with proper settings such as the inclusion of instruction and curated examples, large natural language models such as GPT-3 can identify sexist and racist text at a similar level of specificity to other methods. However, it is possible that if a user intentionally misspells profane words, the models may be less likely to identify such content as problematic. This possibility deserves further investigation due to the tendency for language to change quickly. Furthermore, models might misclassify text that contains identity terms, as they are often associated with harmful statements. Various prompts and settings could be further explored to try to address these issues. Another especially exciting area for further research would be to fine-tune GPT-3 for this task. This means providing many examples initially, which removes the need for examples in the prompt. This is a paid service and would require funding. To better understand why text might be misclassified, it might be useful to prompt GPT-3 to deliver an accompanying explanation for the decision. Another might be to consider a larger dataset of sexist and racist content, as one of the weaknesses of our approach is the relatively small dataset. The extent to which the identification and classification of hate speech can be explained is especially of interest for future work.

@@

\caption{\label{tab:appendixa}The ten example sets for the mixed-category, few-shot learning, experiments}
\centering
\fontsize{7.5}{9.5}\selectfont
\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{18em}>{\raggedright\arraybackslash}p{18em}>{\raggedright\arraybackslash}p{18em}}
\toprule
Set & Example 1 (sexist) & Example 2 (racist) & Example 3 (not hate speech)\\
\midrule
1 & You should know women's sports are a joke & why does that african american monkey hold gun like that? & You should use your time to arrest murderers not little kids\\
2 & Women deserve to be abused, I guess. & Why do negroes tear down their own neighborhoods when a black thug gets killed by law enforcement? Must be because of low IQ. & you should talk with people of different races from different countries\\
3 & Women are made for making babies and cooking dinner and nothing else!!! & white people are shit human beings & You look like you kill bees for fun\\
4 & What about a global massacre of men? Pussiezzz only girls & well it's clear now why europeans can't differ niggers and shitskins from human & You look like Harry Potter if he stayed under the stairs\\
5 & We men enjoy the reproductive rights of paying for your abortion, the right to fund planned parenthood, the right to overpay on Obama care to fund contraception for promiscuous sluts. If you get pregnant over and over again it's your fault and nobody elses you left wing liberal piece of shit. Go be a whore. Keep spreading disease. Half of all black women have herpes. And we have the right to pay for it. You are outrageous. & We whites have higher IQ's than blacks, this is because IQ measures intelligence and we are the more evolved and superior race with a larger brain. & You look kinda dead inside, you parents must not haved loved you.\\
6 & The men are turtles...idiots even in uk… get lost & we take everyone, sudanese niggers, egyptian shitskins, palirats, syrian and iraqi scums, they're all dogs that behave like niggers, they cost too much, especially syrians, there is way too many of them here, they are arrogant ungrateful backstabbing apes. & You have the grace and composure of a rabid hyena\\
7 & That girl still need a good ass whooping, stupid ass bitch!! & U SUCK SHIT YOU BLACK FUCK & You deserve way more subscribers . The shit you say is fucking gold.\\
8 & stone throwing must be legal when against women & This sick, disgusting, white terrorist/fascist killed more than 50 innocent people. & You can see the country is fertile and green. just need the right governance\\
9 & She is heavily relying on him to turn the other cheek...tough talking demon infested woman. & This is considered WHITE in Sweden. No wonder they accepted all those black and muslim immigrants. They are literally color blind. & you are a great brother to abbie, that family is changing the world!\\
10 & Really, I hope she get raped in the future. Raping women should be legal I think & The world would be better without white people because they stole from the black Egyptians in the before christ ages they was poor we wasnt whites  ruins everything for black people/White people have pig dicks and no shape no hips or no booty they have to get plastic surgery as us blacks get it from our mother whites brought skin cancer to america so learn some facts before you try to run us out america when we was here before yall racist ass smelly crackers and dont say you will beat my ass because you cant and if you wanna find out drop your adress & You are a brave man.........for letting them keep the comments enabled\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:zeroshot-racism}Classification of racist statements with zero-shot learning}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
\cmidrule(l{3pt}r{3pt}){2-3}
Actual classification & Not racist & Racist\\
\midrule
Not racist & 19 & 11\\
Racist & 8 & 22\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:zeroshot-sexism}Classification of sexist statements with zero-shot learning}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
\cmidrule(l{3pt}r{3pt}){2-3}
Actual classification & Not sexist & Sexist\\
\midrule
Not sexist & 4 & 26\\
Sexist & 0 & 30\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:zeroshot-hate}Classification of hate speech with zero-shot learning}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
\cmidrule(l{3pt}r{3pt}){2-3}
Actual classification & Not hate speech & Hate speech\\
\midrule
Not hate speech & 23 & 37\\
Hate speech & 8 & 52\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:oneshot-racism}Classification of racist statements with one-shot learning}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
\cmidrule(l{3pt}r{3pt}){2-3}
Actual classification & Not racist & Racist\\
\midrule
Not racist & 13 & 17\\
Racist & 6 & 24\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:oneshot-sexism}Classification of sexist statements with one-shot learning}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
\cmidrule(l{3pt}r{3pt}){2-3}
Actual classification & Not sexist & Sexist\\
\midrule
Not sexist & 13 & 17\\
Sexist & 7 & 23\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:oneshot-hate}Classification of hate speech with one-shot learning}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
\cmidrule(l{3pt}r{3pt}){2-3}
Actual classification & Not hate speech & Hate speech\\
\midrule
Not hate speech & 26 & 34\\
Hate speech & 13 & 47\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:fewshotsingle-racism}Classification of racist statements with single-category few-shot learning}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
\cmidrule(l{3pt}r{3pt}){2-3}
Actual classification & Not racist & Racist\\
\midrule
Not racist & 18 & 12\\
Racist & 7 & 23\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:fewshotsingle-sexism}Classification of sexist statements with single-category few-shot learning}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
\cmidrule(l{3pt}r{3pt}){2-3}
Actual classification & Not sexist & Sexist\\
\midrule
Not sexist & 24 & 6\\
Sexist & 12 & 18\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:fewshotsingle-hate}Classification of hate speech with single-category few-shot learning}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
\cmidrule(l{3pt}r{3pt}){2-3}
Actual classification & Not hate speech & Hate speech\\
\midrule
Not hate speech & 42 & 18\\
Hate speech & 19 & 41\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\title{Detecting Hate Speech with GPT-3 \thanks{Code and data are available at: \url{https://github.com/kelichiu/GPT3-hate-speech-detection}. We gratefully acknowledge the support of Gillian Hadfield, the Schwartz Reisman Institute for Technology and Society, and OpenAI for providing access to GPT-3 under the academic access program. We thank two anonymous reviews and the editor, as well as Amy Farrow, Haoluan Chen, John Giorgi, Mauricio Vargas Sepúlveda, Monica Alexander, Noam Kolt, and Tom Davidson for helpful discussions and suggestions. Please note that we have added asterisks to racial slurs and other offensive content in this paper, however the inputs and outputs did not have these. Comments on the 18 March 2022 version of this paper are welcome at: \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}  }

@@

For zero- and one-shot learning, each set of 120 comments was classified 100 times by GPT-3 in order to assess the variability of classifications at a temperature of 0.3. The reported performance metrics for these settings are the arithmetic means of each metric across all 100 iterations with the corresponding standard error. In some cases, the model outputted responses that were neither ``yes'' nor ``no''. These were counted as ``not applicable'' and omitted from analysis. Specific numbers are reported in the following sections.

@@

The overall results of the zero-shot experiments are presented in Table \ref{tab:zeroshot-summary}, and Appendix \ref{appendixbzeroshot} provides additional detail. Out of 6000 classification for each category, the model has 3231 matches (true positives and negatives) and 2691 mismatches (false positives and negatives) in the sexist category, and 3463 matches and 2504 mismatches in the racist category. In the zero-shot learning setting, the model produced 111 responses that were inadmissible. The model performs more accurately when identifying racist comments, with an average accuracy of 58 per cent (SE = 6.5), compared with identifying sexist comments, with an average accuracy of 55 per cent (SE = 5.2). In contrast, the F1 score for classification of sexist speech is slightly higher on average at 63 per cent (SE = 4.3), compared with an average of 58 per cent (SE = 6.7) for racist speech. The overall ratio of matches and mismatches is 6694:5195. In other words, the average accuracy in identifying hate speech in the zero-shot setting is 56 per cent (SE = 4.6). The model has an average F1 score of 70 per cent (SE = 5.7) in this setting.

@@

\caption{\label{tab:zeroshot-summary}Performance of model in zero-shot learning across 100 classifications of each comment at a temperature of 0.3.}
\centering
\begin{tabular}[t]{>{}llrr}
\toprule
 & Metric & Mean (\%) & Standard Error (\%)\\
\midrule
\textbf{Racism} & Accuracy & 58 & 6.5\\
\textbf{} & Precision & 58 & 6.7\\
\textbf{} & Recall & 59 & 9.2\\
\textbf{} & F1 & 58 & 6.7\\
\textbf{Sexism} & Accuracy & 55 & 5.2\\
\textbf{} & Precision & 53 & 3.7\\
\textbf{} & Recall & 79 & 6.9\\
\textbf{} & F1 & 63 & 4.3\\
\textbf{Overall} & Accuracy & 56 & 4.3\\
\textbf{} & Precision & 55 & 3.5\\
\textbf{} & Recall & 69 & 5.9\\
\textbf{} & F1 & 70 & 5.7\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:oneshot-summary}Performance of model in one-shot learning across 100 classifications of each comment at a temperature of 0.3.}
\centering
\begin{tabular}[t]{>{}llrr}
\toprule
 & Metric & Mean (\%) & Standard Error (\%)\\
\midrule
\textbf{Racism} & Accuracy & 62 & 1.1\\
\textbf{} & Precision & 58 & 0.8\\
\textbf{} & Recall & 80 & 1.2\\
\textbf{} & F1 & 67 & 0.9\\
\textbf{Sexism} & Accuracy & 60 & 1.4\\
\textbf{} & Precision & 57 & 1.1\\
\textbf{} & Recall & 75 & 1.7\\
\textbf{} & F1 & 65 & 1.2\\
\textbf{Overall} & Accuracy & 61 & 0.9\\
\textbf{} & Precision & 58 & 0.7\\
\textbf{} & Recall & 77 & 1.0\\
\textbf{} & F1 & 64 & 1.3\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:fewshotsingle-summary}Performance of model in zero-shot learning across 100 classifications of each comment at a temperature of 0.3.}
\centering
\begin{tabular}[t]{>{}llrr}
\toprule
 & Metric & Mean (\%) & Standard Error (\%)\\
\midrule
\textbf{Racism} & Accuracy & 69 & 1.3\\
\textbf{} & Precision & 67 & 1.3\\
\textbf{} & Recall & 77 & 1.5\\
\textbf{} & F1 & 72 & 1.2\\
\textbf{Sexism} & Accuracy & 73 & 1.4\\
\textbf{} & Precision & 76 & 1.1\\
\textbf{} & Recall & 66 & 2.5\\
\textbf{} & F1 & 71 & 1.8\\
\textbf{Overall} & Accuracy & 71 & 1.0\\
\textbf{} & Precision & 71 & 0.9\\
\textbf{} & Recall & 71 & 1.5\\
\textbf{} & F1 & 65 & 2.2\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/comparison-1.pdf}
\caption{\label{fig:comparison}Comparing classification with and without an instruction}
\end{figure}

@@

In conclusion, with proper settings such as the inclusion of instruction and curated examples, large natural language models such as GPT-3 can identify sexist and racist text at a similar level of specificity to other methods. However, it is possible that if a user intentionally misspells profane words, the models may be less likely to identify such content as problematic. This possibility deserves further investigation due to the tendency for language to change quickly. Furthermore, models might misclassify text that contains identity terms, as they are often associated with harmful statements. Various prompts and settings could be further explored to try to address these issues. Another especially exciting area for further research would be to fine-tune GPT-3 for this task. This means providing many examples initially, which removes the need for examples in the prompt. This is a paid service and would require funding. To better understand why text might be misclassified, it might be useful to prompt GPT-3 to deliver an accompanying explanation for the decision. Another might be to consider a larger dataset of sexist and racist content, as one of the weaknesses of our approach is the relatively small dataset. The extent to which the identification and classification of hate speech can be explained by the model is especially of interest for future work.

@@

\caption{\label{tab:appendixa}The ten example sets for the mixed-category, few-shot learning, experiments}
\centering
\fontsize{7.5}{9.5}\selectfont
\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{18em}>{\raggedright\arraybackslash}p{18em}>{\raggedright\arraybackslash}p{18em}}
\toprule
Set & Example 1 (sexist) & Example 2 (racist) & Example 3 (not hate speech)\\
\midrule
1 & You should know women's sports are a joke & why does that african american monkey hold gun like that? & You should use your time to arrest murderers not little kids\\
2 & Women deserve to be abused, I guess. & Why do negroes tear down their own neighborhoods when a black thug gets killed by law enforcement? Must be because of low IQ. & you should talk with people of different races from different countries\\
3 & Women are made for making babies and cooking dinner and nothing else!!! & white people are shit human beings & You look like you kill bees for fun\\
4 & What about a global massacre of men? Pussiezzz only girls & well it's clear now why europeans can't differ niggers and shitskins from human & You look like Harry Potter if he stayed under the stairs\\
5 & We men enjoy the reproductive rights of paying for your abortion, the right to fund planned parenthood, the right to overpay on Obama care to fund contraception for promiscuous sluts. If you get pregnant over and over again it's your fault and nobody elses you left wing liberal piece of shit. Go be a whore. Keep spreading disease. Half of all black women have herpes. And we have the right to pay for it. You are outrageous. & We whites have higher IQ's than blacks, this is because IQ measures intelligence and we are the more evolved and superior race with a larger brain. & You look kinda dead inside, you parents must not haved loved you.\\
6 & The men are turtles...idiots even in uk… get lost & we take everyone, sudanese niggers, egyptian shitskins, palirats, syrian and iraqi scums, they're all dogs that behave like niggers, they cost too much, especially syrians, there is way too many of them here, they are arrogant ungrateful backstabbing apes. & You have the grace and composure of a rabid hyena\\
7 & That girl still need a good ass whooping, stupid ass bitch!! & U SUCK SHIT YOU BLACK FUCK & You deserve way more subscribers . The shit you say is fucking gold.\\
8 & stone throwing must be legal when against women & This sick, disgusting, white terrorist/fascist killed more than 50 innocent people. & You can see the country is fertile and green.  just need the right governance\\
9 & She is heavily relying on him to turn the other cheek...tough talking demon infested woman. & This is considered WHITE in Sweden. No wonder they accepted all those black and muslim immigrants. They are literally color blind. & you are a great brother to abbie, that family is changing the world!\\
10 & Really, I hope she get raped in the future. Raping women should be legal I think & The world would be better without white people because they stole from the black Egyptians in the before christ ages they was poor we wasnt whites  ruins everything for black people/White people have pig dicks and no shape no hips or no booty they have to get plastic surgery as us blacks get it from our mother whites brought skin cancer to america so learn some facts before you try to run us out america when we was here before yall racist ass smelly crackers and dont say you will beat my ass because you cant and if you wanna find out drop your adress√∞¬ü¬Ü¬ó√Ø¬∏¬è√∞¬ü¬í¬Ø√∞¬ü¬ô¬Ç & You are a brave man.........for letting them keep the comments enabled\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:zeroshot-racism}Classification of racist statements with zero-shot learning}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
\cmidrule(l{3pt}r{3pt}){2-3}
Actual classification & Not racist & Racist\\
\midrule
Not racist & 1688 & 1295\\
Racist & 1209 & 1775\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:zeroshot-sexism}Classification of sexist statements with zero-shot learning}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
\cmidrule(l{3pt}r{3pt}){2-3}
Actual classification & Not sexist & Sexist\\
\midrule
Not sexist & 923 & 2072\\
Sexist & 619 & 2308\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:zeroshot-hate}Classification of hate speech with zero-shot learning}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
\cmidrule(l{3pt}r{3pt}){2-3}
Actual classification & Not hate speech & Hate speech\\
\midrule
Not hate speech & 2611 & 3367\\
Hate speech & 1828 & 4083\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:oneshot-racism}Classification of racist statements with one-shot learning}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
\cmidrule(l{3pt}r{3pt}){2-3}
Actual classification & Not racist & Racist\\
\midrule
Not racist & 1301 & 1699\\
Racist & 608 & 2392\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:oneshot-sexism}Classification of sexist statements with one-shot learning}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
\cmidrule(l{3pt}r{3pt}){2-3}
Actual classification & Not sexist & Sexist\\
\midrule
Not sexist & 1378 & 1622\\
Sexist & 730 & 2170\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:oneshot-hate}Classification of hate speech with one-shot learning}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
\cmidrule(l{3pt}r{3pt}){2-3}
Actual classification & Not hate speech & Hate speech\\
\midrule
Not hate speech & 2679 & 3321\\
Hate speech & 1338 & 4562\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:fewshotsingle-racism}Classification of racist statements with single-category few-shot learning}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
\cmidrule(l{3pt}r{3pt}){2-3}
Actual classification & Not racist & Racist\\
\midrule
Not racist & 1844 & 1156\\
Racist & 683 & 2317\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:fewshotsingle-sexism}Classification of sexist statements with single-category few-shot learning}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
\cmidrule(l{3pt}r{3pt}){2-3}
Actual classification & Not sexist & Sexist\\
\midrule
Not sexist & 2392 & 608\\
Sexist & 1031 & 1969\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:fewshotsingle-hate}Classification of hate speech with single-category few-shot learning}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
\cmidrule(l{3pt}r{3pt}){2-3}
Actual classification & Not hate speech & Hate speech\\
\midrule
Not hate speech & 6000 & 0\\
Hate speech & 0 & 6000\\
\bottomrule
\end{tabular}
\end{table}
